\section{Description of the exercise}

\subsection{Description introduction}

In this second assignment, we have extended the processor from the previous
assignment by changing the datapath into a pipeline. This had the consequence
that pipelines had to be added to the design, as well as write a new control
module to support the pipeline processing.
\paragraph*{}
Additionally, we have
implemented a hazard detection unit and a forwarding unit to guard the
processor from hazards by using correction techniques. The forwarding unit
sends data yet to be written to memory to previous pipeline stages where later
instructions need the current values. The hazard detection unit inserts
``bubbles'' into the pipeline, stalling a selected stage for the duration of a
pipeline clockcycle. It does this to stop a new instruction reading from a
register which a previous instruction is currently writing to.
\paragraph*{}
Both these units have but one intention and consequence, and that is
implementing a more efficient design of the pipelined processor by avoiding
stalls and hazards.

\subsection{Assignment requirements}
\emph{The below text has been copied from the Course Compendium
\cite{compendium}.}\newline
``The major requirement of this assignment is a simple 5-stage pipelined
processor. In general, the processor has the same functional requirements as in
the previous assignment. Additionally, you need to implement diﬀerent hazard
detection and correction techniques. You will also use the same test set up. To
help you on the way, we have made a suggestion from which you can work on. It is
wise to make a processor which relies on the design from the previous assignment
so that you can reuse the test benches and test programs.''
\paragraph*{}
In consequence, we interpreted this to mean that we needed the following:
\begin{enumerate}
	\item A pipelined processor.
	\begin{enumerate}
		\item With five pipeline stages.
	\end{enumerate}
	\item The processors functionality will be based on the functionality of a
``MIPS'' processor.
	\item A Forwarding unit to deal with some of the hazards a pipelined
processor brings.
	\item A Hazard Detection unit to deal with the hazards that occur when a
processor reads and writes in two different pipeline stages.
\end{enumerate}
