Some thought was put into the implementation of the design, especially regarding
how to split the design into its final components. A natural division, which
allowed for a parallell work flow, was to implement each stage of the pipeline
in its own VHDL component. Another idea was to implement the pipeline
registers/buffers in their own VHDL components, but this was dismissed due to
the increased complexity this would have caused the VHDL design.
\paragraph*{}
Another way to implement this design would be to place the pipeline registers in
their own VHDL files, and to include those inside the stage components, but this
would also introduce a lot of unnecessary signals into the stage components
themselves. A final option would be to only have the processor component include
the pipeline registers as separate units, and the rest as one file. This solution would not have
let all of our group members work at once.
\paragraph*{}
It is harder to advocate the specific implementation of the design, since it
does not seem to work perfectly. Most of the implemented ideas worked as intended, and
the problems are mostly related to some unkown behaviour of the DMEM, IMEM and
register file components.
\paragraph*{}
Not knowing whether these would be implemented as registers or not, the
abovementioned components behaved differently than the ones
synthesizing as BRAM and provided confusion and problems when accessing the data
in these. Access to DMEM and IMEM worked as intended in the final product, but a
problem persisted where the register file (or possibly the forwarding units)
only returned zero, instead of the value in the register. This problem made it
hard to test the rest of the functionality and implementation.